Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data

### 2015-02-12 Presentations/Dinamica de Vetores-SP-2015/dengueARS0.tex
fixed typo in the references

\bibitem{pone2011}
Coelho FC, Code\c{c}o CT, Carvalho, LM {E}stimating the Attack Ratio of Dengue 
Epidemics under Time-varying Force of Infection using Aggregated Notification 
Data
\newblock Arxiv. \url{http://arxiv.org/abs/1502.01236}
%\bibAnnoteFile{pone2011}
\end{thebibliography}

>>>>

\bibitem{pone2011}
Coelho FC, Carvalho, LM {E}stimating the Attack Ratio of Dengue 
Epidemics under Time-varying Force of Infection using Aggregated Notification 
Data
\newblock Arxiv. \url{http://arxiv.org/abs/1502.01236}
%\bibAnnoteFile{pone2011}
\end{thebibliography}
